Tor's Usability for Censorship Circumvention

### 2015-04-16 PETS2015-paper/paper.tex
abstract redo

Tor has grown beyond its original purpose and has become an important Internet circumvention tool.
Our work is the first to analyze Tor as a censorship circumvention tool, rather than an anonymous browsing tool. 
We specifically examine one  essential facet for a good censorship circumvention tool: its usability. 
Our analysis the configuration dialog of the browser has new significance because of the new ways Tor is used.
Our talk will describe a future study aimed at evaluating Tor Browser as a tool for censorship circumvention,
 isolating specific browser features in depth in the process. 
To this end, we will conduct a large-scale user study examining hundreds of users 
on how they navigate Tor's configuration wizard to complete seven browsing tasks in three different adversarial settings. 
We solicit feedback in order to improve the representation of our study and its design.
\end{abstract}

@@

We recruited five journalists from Berkeley by reaching out to journalist contacts. 
%Demographics here. 
During the study, we made a video recording of each participant's computer screen
and simultaneously projected it
into another room with Tor developers.
We recorded what they were saying out loud in their cognitive walk through,
and later added these words to the screen videos as subtitles.
The participants also took an exit survey which estimated their familiarity with technology and security. On average, participants took 26 minutes to complete the study ($\sigma = 7$~min).  The result was that people did have difficulty with installing Tor Browser (principally because of the Gatekeeper code-signing feature on OS~X), did not understand what many of the many options meant, and were confused about why certain things were happening. 
Our talk will feature brief highlights of the screen videos.

>>>>

Tor has grown beyond its original purpose as and has 
since become an important Internet circumvention tool.
We specifically examine it usability as a censorship circumvention tool,
an essential facet for adoption and use.  
We focus our analysis on the connection configuration dialog of Tor browser,
as censorship circumvention requires correct transport configurations. %%
Our talk will describe a future study aimed at evaluating 
if and how easily users can circumvent censorship using Tor Browser,
isolating specific browser features to study in the process. 
To this end, we will conduct a large-scale user study examining hundreds of users 
on how they navigate Tor's configuration wizard to complete seven browsing tasks in three different adversarial settings. 
We solicit feedback to improve our study's design.
\end{abstract}

@@

We recruited five journalists from Berkeley by reaching out to journalist contacts. 
%Demographics here. 
During the study, we recorded their screen, what they were saying out loud in their cognitive walk through, and also cast their screen into a room with Tor developers. The participants also took an exit survey which estimated their familiarity with technology and security. On average, participants took 26 minutes to complete the study ($\sigma = 7$~min).  The result was that people did have difficulty with downloading the Tor browser because of the gatekeeper icon, did not understand what many of the many options meant, and were confused about why certain things were happening.
